---
title: "Penguins"
author: "Hannah"
params:
  species: Adelie
---

### Your job: create a parameterized report using data from `penguins.csv`. 
- Your report should contain a ggplot graph of flipper length versus body mass for the **species** that you choose.

- In the `render_functions.R` script, create a function that will render the report for the species you pick, saved as an .html with format 'penguin_report_SPECIESNAME.html'. 

- In the `render_functions.R` script, write a for loop that will automatically render a separate report for *all species* in the data. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
penguins <- read_csv("penguins.csv")

penguin_data <- penguins %>% 
  filter(species == params$species)

ggplot(data = penguin_data, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_line()
```

```{r}
# rmarkdown::render(input = "your_turn.Rmd", params = list(species = "species name"), output_file = "output_file_name.html")

```

```{r}
# loop setup

render_species_report = function(species) {
  rmarkdown::render(
    input = "your_turn.Rmd", # What's the input file to render?
    params = list(species = species), # What are the parameters?
    output_file = paste0(species, "_report", ".html") # What should I name the output file?
  )
}


# loop

species_name <- unique(penguin_data$species)

for (species in species) {
  render_species_report(species)
}
```






